### 2023-02-13 README.Rmd
Update README.Rmd
modern check

<!-- badges: start -->
[![R build status](https://github.com/ropensci/taxadb/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/taxadb/actions)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![Coverage status](https://codecov.io/gh/ropensci/taxadb/branch/master/graph/badge.svg)](https://codecov.io/github/ropensci/taxadb?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/taxadb)](https://cran.r-project.org/package=taxadb)
[![DOI](https://zenodo.org/badge/130153207.svg)](https://zenodo.org/badge/latestdoi/130153207)

<!-- [![peer-review](https://badges.ropensci.org/344_status.svg)](https://github.com/ropensci/software-review/issues/344) -->
<!-- badges: end -->

@@

``` r
install.pacakges("taxadb")
```

@@

Create a local copy of the Catalogue of Life (2018) database:

```{r }
td_create("col", overwrite=FALSE)
```

@@

For instance, *Trochalopteron henrici gucenense* does not resolve to an identifier in ITIS:

```{r}
get_ids("Trochalopteron henrici gucenense") 
```

Using `filter_name()`, we find this is because the name resolves not to zero matches, but to more than one match:

```{r}
filter_name("Trochalopteron henrici gucenense") 
```

```{r}
filter_name("Trochalopteron henrici gucenense")  %>%
  mutate(acceptedNameUsage = get_names(acceptedNameUsageID)) %>% 
  select(scientificName, taxonomicStatus, acceptedNameUsage, acceptedNameUsageID)
```

@@

```{r}
taxa_tbl("col") %>% 
  count(acceptedNameUsageID, sort=TRUE)
```

@@

if(require(codemetar)) codemetar::write_codemeta()
```

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/ropensci/taxadb/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ropensci/taxadb/actions/workflows/R-CMD-check.yaml)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![Coverage status](https://codecov.io/gh/ropensci/taxadb/branch/master/graph/badge.svg)](https://codecov.io/github/ropensci/taxadb?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/taxadb)](https://cran.r-project.org/package=taxadb)
[![DOI](https://zenodo.org/badge/130153207.svg)](https://zenodo.org/badge/latestdoi/130153207)
<!-- badges: end -->

@@

``` r
install.packages("taxadb")
```

@@

Create a local copy of the (current) Catalogue of Life database:

```{r }
td_create("col")
```

@@

For instance, *Agrostis caespitosa* does not resolve to an identifier in ITIS:

```{r}
get_ids("Agrostis caespitosa", "itis") 
```

Using `filter_name()`, we find this is because the name resolves not to zero matches, but is a known synonym to more than one accepted name (as indicated by the accepted name usage id)

```{r}
filter_name('Agrostis caespitosa', 'itis')
```

We can resolve the scientific name to the acceptedNameUsage using `get_names()` on the _accepted_ IDs: (These also correspond to the genus and specificEpithet column, as the classification is always given only based on acceptedNameUsageID).

```{r}
filter_name("Agrostis caespitosa")  %>%
  mutate(acceptedNameUsage = get_names(acceptedNameUsageID)) %>% 
  select(scientificName, taxonomicStatus, acceptedNameUsage, acceptedNameUsageID)
```

@@

```{r}
taxa_tbl("itis") %>% 
  count(acceptedNameUsageID, sort=TRUE)
```

@@

if(require(codemeta)) codemeta::write_codemeta()
```
